AUTOMATED TRANSCRIPTION OF DRUMSOUNDS

### 2017-08-17 Latex/Paper/main.tex
Added abstract, finished implementation and continuted evaluation.

% Title.
% ------
\title{AUTOMATED TRANSCRIPTION OF DRUMSOUNDS}
%
% Single address.
% ---------------
\name{Anyere Bendrien, Maximilian Wagenbach
    \thanks{Thanks to Holger Kirchhof and Tim Flohrer for assistance. Also thanks to TELECOM ParisTech - Dep. TSIe for generously providing the ENST drum test data set.}}
\address{Technical University of Berlin\\
    Audiocommunication Group\\
    Einsteinufer 17, 10587 Berlin}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Stark verkürzte, überblicksartige Darstellung von Forschungsbedarf, Fragestellung, Methode, erwartetem
Ergebnis und Nutzen.
The abstract should contain about 100 to 150 words.
\end{abstract}
%
\begin{keywords}
Non-Negative Matrix Factorization, Drum Transcription, Profit
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

The transcription of the drum track of a song can be useful in many cases.
The simplest would be to generate the sheet music for a song where the original has been lost or is not available.
It can also be used for more sophisticated use cases like a conversion of a audio file to a MIDI sequence (known as Audio-to-MIDI).
For syncing visuals to music in VJing or light show applications (Sound-to-Light) a drum transcription is also an integral part.
Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm [QUELLE].
Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.

@@

Before both inputs are fed into the actual detection the drum sound undergoes some further processing.
This step is marked as \textbf{template extraction} in figure \ref{fig:Flowchart}.
%% TODO: explain transient and shit

@@

Due to the formula \ref{eq:timePoint} we are only able to get the time point within a range of approx. 12 ms.
Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.

@@

@@

As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{\url{http://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
The data set contains recordings of 207 drum tracks split over 3 different drum kits.
In the data set each instrument of the drum kit is recorded separately.
For our purposes we only uses the mixed version of the tracks called ``wet-mix'' which also contains some acoustic elements of the recording room, like reverberation, making it more realistic for real world applications.
Next to the recordings the test data set also contains a annotation file for each drum track, which lists the occurrence an instrument as well as the time point it occurred.
This data was used as the ground truth to compare our algorithm against.

>>>>

% Title.
% ------
\title{AUTOMATED TRANSCRIPTION OF DRUMSOUNDS}
%
% Single address.
% ---------------
\name{Anyere Bendrien, Maximilian Wagenbach
    \thanks{Thanks to Holger Kirchhof and Tim Flohrer for assistance. Also thanks to TELECOM ParisTech - Dep. TSIe for generously providing the ENST drum test data set.}}
\address{Technical University of Berlin\\
    Audiocommunication Group\\
    Einsteinufer 17, 10587 Berlin}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Using math to do magic is easy.
While it is very easy for us humans to find patterns and percussive events in music such a task is very difficult for a computer.
In this research we showed that it is possible for a computer to find the exact time points of drum events in a piece of music by using non-negative matrix factorization.
Generating such a so called drum transcription can have lots of different applications.
By using relatively straightforward math and well established techniques that others before us have researched we hoped to get a reliable drum transcription algorithm.
In doing so we were able to get detection rates of up to 90\%.

%Stark verkürzte, überblicksartige Darstellung von Forschungsbedarf, Fragestellung, Methode, erwartetem Ergebnis und Nutzen.
%The abstract should contain about 100 to 150 words.
\end{abstract}
%
\begin{keywords}
Drum Transcription, Non-Negative Matrix Factorization, Onset Detection%, Profit
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

The transcription of the drum track of a song can be useful in many cases.
The simplest would be to generate the sheet music for a song where the original has been lost or is not available.
It can also be used for more sophisticated use cases like a conversion of a audio file to a MIDI sequence (known as Audio-to-MIDI).
For syncing visuals to music in VJing or light show applications (Sound-to-Light) a drum transcription is also an integral part.
Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm.
Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.

@@

Before both inputs are fed into the actual detection the drum sound undergoes some further processing.
This step is marked as \textbf{template extraction} in figure \ref{fig:Flowchart}.
For our base drum template we chose to only use the transient of the base drum.
This has the advantage that it makes the template independent of the length of the original base drum sound.
As most of the energy is in the transient it is the most relevant part of the base drum sound.
Using only the transient also makes the template somewhat independent of the room it was recorded in, as any possible reverberation or echo is cut off.

@@

Due to the formula \ref{eq:timePoint} we are only able to get the time point within a range of approx. 12 ms (called epsilon).
Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.

@@

The implementation of our algorithm was done in Python using the numpy/scipy library stack. 
As well as the library nimfa\footnote{\url{http://nimfa.biolab.si/}} for NMF calculations.
The entire code repository is licensed under the GPL 3.0 and can be found on GitHub\footnote{\url{https://github.com/Bendrien/AudioContentAnalysis}}.

@@

As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{\url{https://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
The data set contains recordings of 207 drum tracks split over 3 different drum kits.
In the data set each instrument of the drum kit is recorded separately.
For our purposes we only uses the mixed version of the tracks called ``wet-mix'' which also contains some acoustic elements of the recording room, like reverberation, making it more realistic for real world applications.
Next to the recordings the test data set also contains a annotation file for each drum track, which lists the occurrence an instrument as well as the time point it occurred.
This data was used as the ground truth to compare our algorithm against.

In order to evaluate the accuracy of our algorithm we compared the drum events that our algorithm detected with the annotations of the ENST test set.
When comparing the results we took into account the epsilon error margin of approx. 12 ms.

  \begin{table}[h]
    \centering
    \begin{tabular}{l | c c c}
      Drummer  &  1 & 2 & 3 \\
      \# Files &   63 &   75 & 69 \\
      \hline
      Median$_{P}$   & 0.25 & 0.93 & 0.86 \\
      Mean$_{P}$     & 0.27 & 0.89 & 0.80 \\
      $\sigma_P$     & 0.22 & 0.12 & 0.18 \\
      \hline
      Median$_{FP}$   & 0.13 & 0.0 & 0.0 \\
      Mean$_{FP}$     & 0.23 & 0.0 & 0.001 \\
      $\sigma_{FP}$   & 0.29 & 0.0 & 0.001 \\
    \end{tabular}
    \caption{Results of the base drum detection. $P$ represents the true positives and $FP$ the false positives.}
    \label{tab:results}
  \end{table}
